Adaptive Algorithms Employing Continuous Linear Functionals

### 2018-08-25 AutoAlgorithmLinearFunctionalDataVerC.tex
revising figures

 Fig.\ \ref{solfig} shows

@@

Fig. \ref{errfig} shows the sample size needed for ten different error tolerances from $10^{-1}$ to $10^{1}$. If we consider $\varepsilon = 0.1$, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance. For $\varepsilon = 0.1$, the approximate solution and the error in Figure \ref{solfig}. Based on Fig. \ref{solfig}(b), we can obtain the exact errors are less than $0.01 < \varepsilon $.  This shows our algorithm works.

>>>>

Fig.\ \ref{solfig} shows the input function, the solution, the approximate solution, and the error of the approximate solution for $d=3$ and $\varepsilon = 0.1$.  For this example, $ n_{j^\dagger} = 8192$ is sufficient to satisfy the error tolerance, as is clear from Fig.\ \ref{solfig}(d).  Fig. \ref{errfig} shows the sample size, $n_{j^\dagger}$ needed for ten different error tolerances from $0.1$ to $10$. Because the possible sample sizes powers of $2$, some tolerances require the same sample size.

@@
